### 2023-07-17 manuscript.tex
Directly link to changes files, not commits [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c49d0b8ac8f078c226318972b06e8c4a39100bb2.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c49d0b8ac8f078c226318972b06e8c4a39100bb2/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5577316309

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...1f10c12e87d556170c61c2bcd4900dcecb5035ed}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/1f10c12e87d556170c61c2bcd4900dcecb5035ed/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/1f10c12e87d556170c61c2bcd4900dcecb5035ed}{habi/EAWAG-manuscript@1f10c12}
on July 17, 2023.

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...c49d0b8ac8f078c226318972b06e8c4a39100bb2\#files_bucket}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/c49d0b8ac8f078c226318972b06e8c4a39100bb2}{habi/EAWAG-manuscript@c49d0b8}
on July 17, 2023.
